---
title: "A3 - Data Visualization (Incarceration)"
author: "Maoyi Liao"
date: '2022-05-22'
output: html_document
---

```{r include=FALSE} 
library("ggplot2")
library("knitr")
```

```{r setup, include=FALSE}
source("Analysis.R")
```

## Introduction.
In this incarceration data, I choose 8 variables to analyze. They are "year", and the jail population from total and different races, such as "total jail population", "Jail Population Count, Asian American / Pacific Islander", "Jail Population Count, Black", "Jail Population Count, Latinx", "Jail Population Count, Native American", "Jail Population Count, White", and "Unknown or Other Racial Category".

## There are 5 relevant values of interest. 
* The mean of each value in most recent year(2018): 
```{r echo = FALSE}
mean_2018_value
```
* The difference between the max and min mean number in different races:
```{r echo = FALSE}
dif_mean
```
* the highest number of jail population in each race:
```{r echo = FALSE}
highest_value
```
* the lowest number of jail population in each race:
```{r echo = FALSE}
lowest_value
```
* the number of people are incarcerated in different racial groups in different years: 
```{r echo = FALSE}
data_group
```

From this table, we could see the change of jail population in different racial groups within the years.

## Trends over time chart

```{r echo = FALSE}
trend_chart
```
The chart I made shows the jail population in different races increased with time. I created this graph to demonstrate how much and how quickly the jail population grows in different races in comparison. This will be more visually appealing. According to the graph, the total jail population increased significantly between 1995 and 2000, with the white population increasing the most, followed by the black and latinx populations.

## Variable comparison chart

```{r echo = FALSE}
sp_case_death
```
This graph depicts the relationship between the black and total prison populations. I included this chart to see if the increasing jail population in black is related to the overall increasing population. According to the graph, as the total jail population increased, so did the black jail population. As a result, they have a positive relationship.

## Map

```{r echo = FALSE}
p_black
p_white
```
In this project, two maps were created. These two charts were included because they show the jail population in the mainland United States for white and black people separately. We can see from the maps that the density of both white and black jail populations is fairly consistent across the country. The north of the country appears to have a larger jail population than the south of the country in general.




